---
title: "TLMM_JointActionTask"
author: "Giovanna Cuomo"
date: "2024-08-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CODE BOOK & DESCRIPTION
This script contains the analyses conducted on data related to participants who took part in our study for the Joint Action Task.
In three different experiments, participants were presented with two virtual partners during the joint action task: an out-group (Black) or an in-group (White) avatar (the control condition). The instruction was to synchronize with the partner to gasp together a bottle-shaped object in front of them, performing the Same or Opposite movement relative to the avatar. A recent study has already proven how a partner’s racial membership can modulate interactive behaviors (Sacheli et al., 2015). To investigate the role of mPFC (vs Vertex, vs vPM) in coordinating with an out-group partner after a virtual inhibition of the area, before the joint action task, a continuous theta burst stimulation was administered (cTBS; Huang et al., 2005).

Hypotheses
1) Partner's ethnicity modulates people's ability to coordinate with them for shared goals.
2) mPFC inhibition reduces predictive simulation during joint action with an ethnic out-group member, deteriorating the interactive performance.
3) mPFC inhibition increases explicit and implicit racial bias.

Preprocessing
The raw data were cleaned as follows: 
1) trials in which participants failed to grasp the bottle-shaped object correctly were excluded from the analyses (i.e., when the touch-sensitive plates were not correctly pressed); 
2) trials when participants did not follow the instructions, and grasped the object on the wrong half the trial was discarded; 
3) in a similar way, we did not include in the analyses those trials in which participants started their movement before the audio instruction was given;
4) catch trials (i.e., when the virtual partner switched movement direction) from the analyses.
5) outliers trial values 2.5 standard deviations above or below the mean for each subject within each condition

Independent Variables:
Site (mPFC vs vPM vs Vertex)
Virtual partner Ethnicity (Black vs White)
Movement (Same vs Opposite)
Experiment (1, 2 or 3)

Dependent Variables:
Grasping Asynchrony (GA), i.e., the absolute value of the difference between the time of the thumb-index contact on the bottle-shaped object for the virtual partner and the participant.
Movement Time (MT), i.e., the difference between the time the participant released the starting button and the time of their thumb-index contact with the object.
Reaction Time (RT), i.e., the time passed between the end of the audio instruction and the moment the participant released the stating button.

MLMMs
In constructing the MLMMs that follows, we performed a “stepwise backward” selection process for the random effects. Starting from a structure that included all the relevant effects and interactions, we systematically removed terms based on singularity to optimize model fit and ensure the convergence of the model. Post-hoc comparisons were conducted utilizing the 'Estimated Marginal Means' R package (Lenth, 2020), employing the ‘emmeans’ and ‘emtrends’ functions to further investigate significant interactions. Bonferroni correction for multiple comparisons was applied. 


First, we load packages we need for analyses 
#PACKAGES
```{r}
library (tidyverse) #for data handling
library(readxl) #to read excel files
library(writexl)  #to export data as excel file 
library(lme4) 
library(emmeans) 
library(ggplot2)
library(rstatix)
library(stats)
library(dplyr)
library(yarrr)
library(xlsx)

options(scipen=999)
```

##STUDY 1 & 3
```{r}
dati_tms = read.xlsx("data_1_3.xlsx", sheetIndex = 1)
```

Specifying the factors
```{r}
dati_tms$sito = as.factor(dati_tms$sito)
dati_tms$bw = as.factor(dati_tms$bw)
dati_tms$Movement = as.factor(dati_tms$Movement)
dati_tms$Grasp = as.factor(dati_tms$Grasp)
dati_tms$Subject = as.factor(dati_tms$Subject)
```

#Grasping Asynchrony
```{r}
ASY_model = lmer(Asynchrony ~  Exp * bw * sito * Movement +
                            (1+ sito*bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dati_tms)
#summary(ASY_model)
isSingular(ASY_model)
Anova(ASY_model)
```

residuals check
```{r}
res = residuals(ASY_model)
plot(density(res))
plot(ASY_model)
qqnorm(residuals(ASY_model))
qqline(residuals(ASY_model))
```

significant interactions post-hocs
```{r}
#emmeans/posthoc
emmeans_interaction <- emmeans(ASY_model, ~ Exp * sito)

posthoc_interaction <- pairs(emmeans_interaction, adjust = "bonferroni")

summary(posthoc_interaction)
```

plot dataset
```{r}
pirateplot(formula = Asynchrony ~ bw + sito + Exp, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)
```

main effect of  Movement - plot
```{r}
pirateplot(formula = Asynchrony ~ Movement, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)
```


#Since data were not normal: Alternative - GA log
```{r}
dati_tms$Asynchrony_log = log(dati_tms$Asynchrony + 225)
```

run LMM log
```{r}
ASY_model3 = lmer(Asynchrony_log ~  Exp * bw * sito * Movement +
                            (1+bw*sito|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dati_tms)
summary(ASY_model3)
isSingular(ASY_model3)
Anova(ASY_model3)
```

significant interactions post-hocs
```{r}
#emmeans/posthoc
emmeans_interaction <- emmeans(ASY_model3, ~ Exp * sito)

posthoc_interaction <- pairs(emmeans_interaction, adjust = "bonferroni")

summary(posthoc_interaction)
```

Significant effects  - plot
```{r}
pirateplot(formula = Asynchrony_log ~ Movement, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)

```

mean and ds
```{r}
library(dplyr)

summary_stats_asy <- dati_tms %>%
  group_by(Movement) %>%
  summarise(
    mean_Asy = mean(Asynchrony_log, na.rm = TRUE),      # Calcola la media
    sd_Asy = sd(Asynchrony_log, na.rm = TRUE)           # Calcola la deviazione standard
  )

summary_stats_asy1 <- dati_tms %>%
  group_by(Movement) %>%
  summarise(
    mean_Asy = mean(Asynchrony, na.rm = TRUE),      # Calcola la media
    sd_Asy = sd(Asynchrony, na.rm = TRUE)           # Calcola la deviazione standard
  )

```

residuals check
```{r}
res = residuals(ASY_model3)
plot(density(res))
plot(ASY_model3)
qqnorm(residuals(ASY_model3))
qqline(residuals(ASY_model3))
```


#Movement Time
```{r}
MT_model = lmer(MovTime ~  Exp * bw * sito * Movement +
                            (1+sito*bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dati_tms)
summary(MT_model)
isSingular(MT_model)
Anova(MT_model)
```

residuals check
```{r}
res = residuals(MT_model)
plot(density(res))
plot(MT_model)
qqnorm(residuals(MT_model))
qqline(residuals(MT_model))
```

plot dataset
```{r}
pirateplot(formula = MovTime ~ bw + sito + Movement, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Movement Time", xlab = "",#titles for x and y axes
)
```

plot main effect
```{r}
pirateplot(formula = MovTime ~ Movement, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Movement Time", xlab = "",#titles for x and y axes
)
```

mean and ds
```{r}
library(dplyr)

summary_stats_asy <- dati_tms %>%
  group_by(Movement) %>%
  summarise(
    mean_MovTime = mean(MovTime, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(MovTime, na.rm = TRUE)           # Calcola la deviazione standard
  )
```


#Start - RT
```{r}
RT_model = lmer(Start ~  Exp * bw * sito * Movement +
                            (1+sito*bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dati_tms)
summary(RT_model)
isSingular(RT_model)
Anova(RT_model)
```

check residuals
```{r}
res = residuals(RT_model)
plot(density(res))
plot(RT_model)
qqnorm(residuals(RT_model))
qqline(residuals(RT_model))
```

posthocs
```{r}
#emmeans/posthoc
emmeans_interaction1 <- emmeans(RT_model, ~ Exp * Movement)
emmeans_interaction2 <- emmeans(RT_model, ~ Movement * Exp * bw)

posthoc_interaction1 <- pairs(emmeans_interaction1, adjust = "bonferroni")
posthoc_interaction2 <- pairs(emmeans_interaction2, adjust = "bonferroni")

summary(posthoc_interaction1)
summary(posthoc_interaction2)
```

means, ds
```{r}

summary_statsRT <- dati_tms %>%
  group_by(bw) %>%
  summarise(
    mean_start = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_start = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )
```


dataset plot
```{r}
pirateplot(formula = Start ~ bw + sito + Movement, #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)
```

main effect plot
```{r}
pirateplot(formula = Start ~ bw , #dependent variable ~ independent
           data = dati_tms,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)
```




##STUDIO 2
```{r}
EXP2 = read.xlsx("data_2.xlsx", sheetIndex = 1)
```

Factor Specification
```{r}
EXP2$sito = as.factor(EXP2$sito)
EXP2$bw = as.factor(EXP2$bw)
EXP2$Grasp= as.factor(EXP2$Grasp)
EXP2$Movement = as.factor(EXP2$Movement)
EXP2$Subject = as.factor (EXP2$Subject)
```

#Grasping Asynchrony
```{r}
ASY_EXP2 = lmer (Asynchrony ~  bw * sito * Movement +
                               (1|Subject), control = lmerControl(optimizer = "bobyqa"),
                             data = EXP2)
isSingular(ASY_EXP2)
summary(ASY_EXP2)
Anova(ASY_EXP2)
```
check residuals
```{r}
res = residuals(ASY_EXP2)
plot(density(res))
plot(ASY_EXP2)
qqnorm(residuals(ASY_EXP2))
qqline(residuals(ASY_EXP2))
```

data plot
```{r}
pirateplot(formula = Asynchrony ~ bw + sito + Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "Experiment 2",#titles for x and y axes
)
```

Main effect Site
```{r}
pirateplot(formula = Asynchrony ~ sito, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "Experiment 2",#titles for x and y axes
)
```

Main effect Movement
```{r}
pirateplot(formula = Asynchrony ~ Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "Experiment 2",#titles for x and y axes
)
```

mean and ds
```{r}

statsGA_EXP2 <- EXP2 %>%
  group_by(Movement) %>%
  summarise(
    mean_asy = mean(Asynchrony, na.rm = TRUE),      # Calcola la media
    sd_asy = sd(Asynchrony, na.rm = TRUE)           # Calcola la deviazione standard
  )

statsGA_EXP2_sito <- EXP2 %>%
  group_by(sito) %>%
  summarise(
    mean_sito = mean(Asynchrony, na.rm = TRUE),      # Calcola la media
    sd_sito = sd(Asynchrony, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

#Since data were not normal: Alternative - GA log
```{r}
EXP2$Asynchrony_log = log(EXP2$Asynchrony + 225)
```

run LMM log
```{r}
ASY_model_studio2 = lmer(Asynchrony_log ~  bw * Movement * sito +
                            (1|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = EXP2)

#summary(ASY_model_studio2)
isSingular(ASY_model_studio2)
Anova(ASY_model_studio2)
```

residuals check
```{r}
res = residuals(ASY_model_studio2)
plot(density(res))
plot(ASY_model_studio2)
qqnorm(residuals(ASY_model_studio2))
qqline(residuals(ASY_model_studio2))
```
data plots
```{r}
pirateplot(formula = Asynchrony_log ~  bw, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)

pirateplot(formula = Asynchrony_log ~  Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)
```


Means, ds
```{r}

log_statsASY2 <- EXP2 %>%
  group_by(bw) %>%
  summarise(
    mean_bw = mean(Asynchrony_log, na.rm = TRUE),      # Calcola la media
    sd_bw = sd(Asynchrony_log, na.rm = TRUE)           # Calcola la deviazione standard
  )

log_statsASY_m2 <- EXP2 %>%
  group_by(Movement) %>%
  summarise(
    mean_m = mean(Asynchrony_log, na.rm = TRUE),      # Calcola la media
    sd_m = sd(Asynchrony_log, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

#Movement Time
```{r}
MT_EXP2 = lmer(MovTime ~  bw * sito * Movement +
                            (1+sito*bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = EXP2)
summary(MT_EXP2)
isSingular(MT_EXP2)
Anova(MT_EXP2)
```

Posthocs
```{r}
#emmeans/posthoc
emmeans_interaction <- emmeans(MT_EXP2, ~ bw * sito)
emmeans_interaction1 <- emmeans(MT_EXP2, ~ bw * Movement)
emmeans_interaction2 <- emmeans(MT_EXP2, ~ Movement * sito)


posthoc_interaction <- pairs(emmeans_interaction, adjust = "bonferroni")
posthoc_interaction1 <- pairs(emmeans_interaction1, adjust = "bonferroni")
posthoc_interaction2 <- pairs(emmeans_interaction2, adjust = "bonferroni")


summary(posthoc_interaction)
summary(posthoc_interaction1)
summary(posthoc_interaction2)

```

Control residuals distributions 
```{r}
res = residuals(MT_EXP2)
plot(density(res))
plot(MT_EXP2)
qqnorm(residuals(MT_EXP2))
qqline(residuals(MT_EXP2))
```

data plots
```{r}
pirateplot(formula = MovTime ~ bw + sito + Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Movement Time", xlab = "Experiment 2",#titles for x and y axes
)
```

#Start - RT
```{r}
RT_EXP2 = lmer(Start ~ bw * sito * Movement +
                            (1+sito*bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = EXP2)
summary(RT_EXP2)
isSingular(RT_EXP2)
Anova(RT_EXP2)
```

Control residual distribution
```{r}
res = residuals(RT_EXP2)
plot(density(res))
plot(RT_EXP2)
qqnorm(residuals(RT_EXP2))
qqline(residuals(RT_EXP2))
```

Posthocs
```{r}
#emmeans/posthoc
emmeans_interaction <- emmeans(RT_EXP2, ~ bw * sito * Movement)

posthoc_interaction <- pairs(emmeans_interaction, adjust = "bonferroni")

summary(posthoc_interaction)
```

Mean and ds
```{r}

summary_statsRT_EXP2 <- EXP2 %>%
  group_by(Movement) %>%
  summarise(
    mean_MovTime = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )
```


Dataplots
```{r}
pirateplot(formula = Start ~ bw + sito + Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Time", xlab = "Experiment 2",#titles for x and y axes
)
```


Main Effect Plot
```{r}
pirateplot(formula = Start ~ Movement, #dependent variable ~ independent
           data = EXP2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Time", xlab = "Experiment 2",#titles for x and y axes
)
```


##ALL STUDIES
```{r}
dataset_2 = read.xlsx("dataset_2.xlsx", sheetIndex = 1)
```

factors declaration
```{r}
dataset_2$sito = as.factor(dataset_2$sito)
dataset_2$bw = as.factor(dataset_2$bw)
dataset_2$Movement = as.factor(dataset_2$Movement)
dataset_2$Grasp = as.factor(dataset_2$Grasp)
dataset_2$Subject = as.factor(dataset_2$Subject)
```

#Grasping Asynchrony
```{r}
ASY_model_3studi = lmer(Asynchrony ~  Exp * bw * Movement + sito +
                               (1+bw+sito|Subject), control = lmerControl(optimizer = "bobyqa"),
                             data = dataset_2)
#summary(ASY_model_3studi)
isSingular(ASY_model_3studi)
Anova(ASY_model_3studi)
```

residuals check
```{r}
res = residuals(ASY_model_3studi)
plot(density(res))
plot(ASY_model_3studi)
qqnorm(residuals(ASY_model_3studi))
qqline(residuals(ASY_model_3studi))
```
means, ds
```{r}

summary_statsASY_ALL <- dataset_2 %>%
  group_by(Movement) %>%
  summarise(
    mean_Mov = mean(Asynchrony, na.rm = TRUE),      # Calcola la media
    sd_Mov = sd(Asynchrony, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

data plots
```{r}
pirateplot(formula = Asynchrony ~  Movement, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)
```

#Since data were not normal: Alternative - GA log
```{r}
dataset_2$Asynchrony_log = log(dataset_2$Asynchrony + 225)
```

run LMM log
```{r}
ASY_model_3studi2 = lmer(Asynchrony_log ~  Exp * bw * Movement + sito +
                            (1+bw+sito|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dataset_2)

#summary(ASY_model_3studi2)
isSingular(ASY_model_3studi2)
Anova(ASY_model_3studi2)
```

residuals check
```{r}
res = residuals(ASY_model_3studi2)
plot(density(res))
plot(ASY_model_3studi2)
qqnorm(residuals(ASY_model_3studi2))
qqline(residuals(ASY_model_3studi2))
```
data plots
```{r}
pirateplot(formula = Asynchrony_log ~  Movement, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Grasping Asynchrony", xlab = "",#titles for x and y axes
)
```


means, ds
```{r}

log_statsASY_ALL <- dataset_2 %>%
  group_by(Movement) %>%
  summarise(
    mean_Mov = mean(Asynchrony_log, na.rm = TRUE),      # Calcola la media
    sd_Mov = sd(Asynchrony_log, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

#Movement Time
```{r}
MT_model_3studi = lmer(MovTime ~  Exp * bw * Movement +
                            (1+bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dataset_2)
#summary(MT_model_3studi)
isSingular(MT_model_3studi)
Anova(MT_model_3studi)
```
check residuals
```{r}
res = residuals(MT_model_3studi)
plot(density(res))
plot(MT_model_3studi)
qqnorm(residuals(MT_model_3studi))
qqline(residuals(MT_model_3studi))
```

means, ds
```{r}

summary_statsMT_Exp <- dataset_2 %>%
  group_by(Exp) %>%
  summarise(
    mean_MovTime = mean(MovTime, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(MovTime, na.rm = TRUE)           # Calcola la deviazione standard
  )

summary_statsMT <- dataset_2 %>%
  group_by(Movement) %>%
  summarise(
    mean_MovTime = mean(MovTime, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(MovTime, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

posthocs
```{r}
#emmeans/posthoc
emmeans_Experiment <- emmeans(MT_model_3studi, ~ Exp)

posthoc_Experiment <- contrast(emmeans_Experiment, adjust = "bonferroni")

summary(posthoc_Experiment)
```
main effects plots
```{r}
pirateplot(formula = MovTime ~ Movement, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Movement Time", xlab = "",#titles for x and y axes
)

pirateplot(formula = MovTime ~ Exp, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Movement Time", xlab = "",#titles for x and y axes
)
```

#Start - RT
```{r}
RT_model_3studi = lmer(Start ~  Exp * bw * Movement +
                            (1+bw|Subject), control = lmerControl(optimizer = "bobyqa"),
                          data = dataset_2)
#summary(RT_model_3studi)
isSingular(RT_model_3studi)
Anova(RT_model_3studi)
```
check residuals
```{r}
res = residuals(RT_model_3studi)
plot(density(res))
plot(RT_model_3studi)
qqnorm(residuals(RT_model_3studi))
qqline(residuals(RT_model_3studi))
```

posthocs
```{r}
#emmeans/posthoc
RT_emmeans_interaction <- emmeans(RT_model_3studi, ~ Exp * Movement)
RT_emmeans_Experiment <- emmeans(MT_model_3studi, ~ Exp)


posthoc_interaction <- pairs(RT_emmeans_interaction, adjust = "bonferroni")
posthoc_Experiment <- contrast(RT_emmeans_Experiment, adjust = "bonferroni")

summary(posthoc_interaction)
summary(posthoc_Experiment)
```

means and ds
```{r}

statsRT_Exp <- dataset_2 %>%
  group_by(Exp) %>%
  summarise(
    mean_MovTime = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )

statsRT_Mov <- dataset_2 %>%
  group_by(Movement) %>%
  summarise(
    mean_MovTime = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )

statsRT_bw <- dataset_2 %>%
  group_by(bw) %>%
  summarise(
    mean_MovTime = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )

statsRT_interaction <- dataset_2 %>%
  group_by(Exp, Movement) %>%
  summarise(
    mean_MovTime = mean(Start, na.rm = TRUE),      # Calcola la media
    sd_MovTime = sd(Start, na.rm = TRUE)           # Calcola la deviazione standard
  )
```

significant results plots 
```{r}
pirateplot(formula = Start ~ Movement, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)

pirateplot(formula = Start ~ Exp, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)

pirateplot(formula = Start ~ bw, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)

pirateplot(formula = Start ~ Exp + Movement, #dependent variable ~ independent
           data = dataset_2,  #data
           theme = 3, #set theme
           gl.col = "white",
           ylab = "Reaction Times", xlab = "",#titles for x and y axes
)
```
